\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-23 paper.tex
added a draft table with stats
commented out acks
update in table

\usepackage{url}
\usepackage{listings}
\usepackage{xspace}

@@

@@

We present a new methodology for systematically testing distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem.

@@

\section{Acknowledgments}

A polite author always includes acknowledgments.  Thank everyone,
especially those who funded the work.

\section{Availability}

It's great when this section says that MyWonderfulApp is free software, 
available via anonymous FTP from ... Also, it's even greater when you can
write that information is also  available on the Wonderful homepage at

>>>>

%\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{pifont}

\usepackage{url}
\usepackage{multirow}
\usepackage{listings}
\usepackage{booktabs}
%\usepackage{tikz}
\usepackage{xspace}

@@

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

@@

We present a new methodology for systematically testing distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem. \PDComment{we now have many bugs in Matt's system too.}

@@

%\section{Acknowledgments}

%Draft.
